---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Claranghc"
date: "May 10, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##Introduction

This course Project have 2 parts.

- Shiny app 
- App presentation


The app developed of the assignment demo is avalilable at: https://claranghc.shinyapps.io/assignment3/

Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/ClaraNgHC/Course-Project-Shiny-Application-and-Reproducible-Pitch

## Simple Currency exchange

Taking USD as the main currency in this app. This app is using the USD rate as at 22/4/2017

Listed are 4 countries that can select from to check on the exchange rate.

- Malaysia
- Singapore
- Thailand
- Australia


##Calculation part

###Formula used

Amount of USD * Rate for the selected country

### Example

Country = Malaysia (MYR)

- USD entered = 10
- MYR rate = 4.40

Result  = 10 * 4.40
        = 44 MYR

USD 10 = MYR 44

## R Code

```{r echo = FALSE}
## Putting in example    
Currency <- "MYR"
USDAmt <- 10
```
```{r echo =TRUE}    
##USD exchange Rate base on the country selected dated as 22/4/2017
    USDMYR <- 4.40
    USDSGD <- 1.40
    USDBAHT <- 34.36
    USDAUD <- 1.33

#Doing simple calculations 
     if (Currency == "MYR")
      Result1 <- USDAmt * USDMYR
    if (Currency == 'SG')
      Result1 <- USDAmt * USDSGD
    if (Currency == 'Thai')
      Result1 <- USDAmt * USDBAHT
    if (Currency == 'AUS')
      Result1 <- USDAmt * USDAUD

```